PyChrono and gym-chrono: a Deep Reinforcement Learning framework leveraging Multibody Dynamics to \\ control Autonomous Vehicles and Robots.

### 2020-11-30 2021/NODYCON_PyChrono/author.tex
Fix path to figures

\begin{figure}[ht]
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{ProcSci_TeX/Figures/pendulum.png}
    \caption{Pendulum}
    \label{fig:pendulum}
 \end{minipage}
 \hspace{0.4cm}
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{ProcSci_TeX/Figures/ant.png}
    \caption{Ant}
    \label{fig:ant}
 \end{minipage}
\end{figure}

@@

\begin{figure}[ht]
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{ProcSci_TeX/Figures/Comau.jpg}
    \caption{Robotic Arm Environment}
    \label{fig:Comau}
 \end{minipage}
 %\hspace{0.4cm}
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{ProcSci_TeX/Figures/obst_aovid.png}
    \caption{Obstacle Avoidance Environment}
    \label{fig:Obst_avoid}
 \end{minipage}
\end{figure}

@@

\begin{figure}[ht]
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{ProcSci_TeX/Figures/Hexapod.jpg}
    \caption{Hexapod Environment}
    \label{fig:Hexa}
 \end{minipage}
 %\hspace{0.4cm}
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{ProcSci_TeX/Figures/hexa_rew.png}
    \caption{Hexapod Reward Progression}
    \label{fig:Hexa_rew}
 \end{minipage}
\end{figure}

@@

\begin{figure}[ht]
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{ProcSci_TeX/Figures/hallway.png}
    \caption{Hallway Cone Track Environment}
    \label{fig:Hallway}
 \end{minipage}
 %\hspace{0.4cm}
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{ProcSci_TeX/Figures/hallway_rewards.pdf}
    \caption{Hallway Cone Track Reward Progression}
    \label{fig:Hallway_rew}
 \end{minipage}
\end{figure}

>>>>

\begin{figure}[ht]
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{Figures/pendulum.png}
    \caption{Pendulum}
    \label{fig:pendulum}
 \end{minipage}
 \hspace{0.4cm}
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{Figures/ant.png}
    \caption{Ant}
    \label{fig:ant}
 \end{minipage}
\end{figure}

@@

\begin{figure}[ht]
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{Figures/Comau.jpg}
    \caption{Robotic Arm Environment}
    \label{fig:Comau}
 \end{minipage}
 %\hspace{0.4cm}
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{Figures/obst_aovid.png}
    \caption{Obstacle Avoidance Environment}
    \label{fig:Obst_avoid}
 \end{minipage}
\end{figure}

@@

\begin{figure}[ht]
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{Figures/Hexapod.jpg}
    \caption{Hexapod Environment}
    \label{fig:Hexa}
 \end{minipage}
 %\hspace{0.4cm}
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{Figures/hexa_rew.png}
    \caption{Hexapod Reward Progression}
    \label{fig:Hexa_rew}
 \end{minipage}
\end{figure}

@@

\begin{figure}[ht]
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{Figures/hallway.png}
    \caption{Hallway Cone Track Environment}
    \label{fig:Hallway}
 \end{minipage}
 %\hspace{0.4cm}
 \begin{minipage}[b]{0.6\linewidth}
    \centering
    \includegraphics[width=0.75\textwidth]{Figures/hallway_rewards.pdf}
    \caption{Hallway Cone Track Reward Progression}
    \label{fig:Hallway_rew}
 \end{minipage}
\end{figure}
